Demand Forecasting of individual Probability Density Functions with Machine Learning

### 2020-08-17 LaTex/paper.tex
reviewed abstract and introduction

\begin{abstract}
Demand forecasting is a central component for many aspects of supply chain operations as it provides crucial input for subsequent decision making like ordering processes. While machine learning methods can significantly improve prediction accuracy over traditional time series forecasting, the calculated predictions are often mere point estimations for the conditional mean of the underlying probability distribution, and the most powerful approaches, like deep learning, are usually opaque in terms of how its individual predictions can be interpreted. Using the novel supervised machine learning method ``Cyclic Boosting'', complete individual probability density functions in form of negative binomial distributions can be predicted instead of simple point estimates. While metrics evaluating simple point estimates are widely used, methods for assessing the accuracy of predicted distributions are rare and this work proposes new techniques for both qualitative and quantitative evaluation methods. Additionally, each single prediction obtained with this framework is explainable, which is a major benefit in practice as individual forecasts can be understood by the practitioner and ``black-box'' models can be avoided. 
\end{abstract}

@@

Demand forecasting is one of the main challenges for retailers and at the core of business operations. Due to its stochastic nature, demand is difficult to forecast as it depends on many influencing factors and the realized demand can be interpreted as a random variable that is described by an appropriate probability density function (PDF). In order to make operational decisions, an optimal point estimator has to be defined, that can be used to derive ordering decisions used in the replenishment process of the retailer. Demand estimation is further complicated by the fact that retailers typically only observe realized sales rather than the actual demand, and in case the demand exceeds the current stock level the data become censored. The ordering decision process is complicated by a range of factors: Even in the case of perfect demand forecasts, the decision maker has to consider lot-sizes defined by the wholesaler or manufacturer as well as to balance conflicting metrics to reach an optimal decision: Ordering too few items may result in stock-out situations leading to unrealized demand and unsatisfied customers. Ordering too many items results in excess inventory which increases transport and storage costs and, in the case of perishable goods, excessive waste, as spoilt items need to be disposed of at additional cost and potentially even environmental impact. This situation is particularly noticeable in the so called "ultra-fresh'' category, which includes items such as bakery products, ready-meals, fresh diary products, or certain meat products such as ground meat. These items typically have a shelf-life ranging from less than a business day to a few business days at most, with a continuous spectrum in between, depending on the exact item. In many situations, additional constraints have to be considered to reach an optimal ordering decision: Delivery cycles of items may vary depending on the type of item and the wholesaler or manufacturer from which they are procured. Retailers also operate at a given service level to guarantee that a certain level of demand can be fulfilled. The exact service level typically depends on the overall business policy of the retailer and may also depend on individual products, ranging from "never-out-of-stock'' items to a service level exceeding e.g. 90\%.

The availability of Big Data allows capturing, storing and processing a vast amount of data associated with demand, such as historic sales records, information about promotional events or advertisements, pricing information, local weather at retail locations, seasonal information as well as a wide range of further variables. Modern machine learning algorithms can then be used to predict the per-item demand distribution, corrected for censored data, from which an optimal point estimator can be derived to be used in the subsequent ordering decision. It is important to note that demand as a random variable is not identically and independently distributed (i.i.d.). While the probability distribution describing the demand can be attributed to a given family or parameterization, the exact parameters vary: Seasonal effects, finite life cycles of products and the introduction of new products influence the demand distribution, as well as the local weather at the retail location or the retail location itself in terms of size, assortment range, customer diversity and other factors. The retailers themselves also actively influence demand by using advertisements to highlight products, offering rebates or discounts for specific products as well as pursuing an active pricing strategy. This means that while we can generally assume that demand follows a specific type of probability distribution, its parameters are unique to the  instance for which an estimate is required. For example, the probability distribution governing the demand of a particular item is specific to the item, date and retail location for which the forecast is made and depends on a wide range of further influencing factors.

The remainder of the paper is organized as follows: We first review the relevant literature and existing work in sec. \ref{sec:LitRev}. We then describe our method to predict individual negative binomial PDFs by means of a parametric approach including two distinct machine learning models for mean of variance in sec. \ref{sec:pdfEstimation}. After that we describe methods for the qualitative and quantitative evaluation of PDF predictions in sec. \ref{sec:pdfEvaluation}. And finally, we present a demand forecasting example to show an application of our methods in sec. \ref{sec:example}.

>>>>

\begin{abstract}
Demand forecasting is a central component for many aspects of supply chain operations, as it provides crucial input for subsequent decision making like ordering processes. While machine learning methods can significantly improve prediction accuracy over traditional time series forecasting, the calculated predictions are often mere point estimations for the conditional mean of the underlying probability distribution, and the most powerful approaches, like deep learning, are usually opaque in terms of how its individual predictions can be interpreted. Using the novel supervised machine learning method ``Cyclic Boosting'', complete individual probability density functions in form of negative binomial distributions can be predicted instead of simple point estimates. While metrics evaluating simple point estimates are widely used, methods for assessing the accuracy of predicted distributions are rare and this work proposes new techniques for both qualitative and quantitative evaluation methods. Additionally, each single prediction obtained with this framework is explainable, which is a major benefit in practice, as individual forecasts can be understood by the practitioner and ``black-box'' models can be avoided. 
\end{abstract}

@@

Demand forecasting is one of the main challenges for retailers and at the core of supply chain business operations. Due to its stochastic nature, demand is difficult to forecast. It depends on many influencing factors and the realized demand can be interpreted as a random variable that is described by an appropriate probability density function (PDF). In order to make operational decisions, an optimal point estimator has to be defined, that can be used to derive ordering decisions in the replenishment process of the retailer. Demand estimation is further complicated by the fact that retailers typically only observe realized sales rather than the actual demand, and in case the demand exceeds the current stock level the data become censored.

The ordering decision process is complicated by a range of factors: Even in the case of perfect demand forecasts, the decision maker has to consider lot-sizes defined by the wholesaler or manufacturer as well as to balance conflicting metrics to reach an optimal decision. Ordering too few items may result in stock-out situations leading to unrealized demand and unsatisfied customers. Ordering too many items results in excess inventory, which increases transport and storage costs and, in the case of perishable goods, excessive waste, as spoilt items need to be disposed of at additional cost and potentially even environmental impact. This situation is particularly noticeable in the so called "ultra-fresh'' category, which includes items such as bakery products, ready-meals, fresh diary products, or certain meat products such as ground meat. These items typically have a shelf-life ranging from less than a business day to a few business days at most, with a continuous spectrum in between, depending on the exact item. In many situations, additional constraints have to be considered to reach an optimal ordering decision: Delivery cycles of items may vary depending on the type of item and the wholesaler or manufacturer from which they are procured. Retailers also operate at a given service level to guarantee that a certain level of demand can be fulfilled. The exact service level typically depends on the overall business policy of the retailer and may also depend on individual products, ranging from "never-out-of-stock'' items to a service level exceeding e.g. 90\%.

The availability of Big Data allows capturing, storing, and processing a vast amount of data associated with demand, such as historic sales records, information about promotional events or advertisements, pricing information, local weather at retail locations, seasonal information, as well as a wide range of further variables. Modern machine learning algorithms can then be used to predict the per-item-location demand distribution, corrected for censored data, from which an optimal point estimator can be derived to be used in the subsequent ordering decision. Demand forecasting is an application of time series forecasting and it is important to note that demand as a random variable is not identically and independently distributed (i.i.d.) between different items and locations. While the probability distribution describing the demand can be attributed to a given family or parameterization, the exact parameters vary: Seasonal effects, finite life cycles of products, and the introduction of new products influence the demand distribution, as well as the local weather at the retail location or the retail location itself in terms of size, assortment range, customer diversity, and other factors. The retailers themselves also actively influence demand by using advertisements to highlight products, offering rebates or discounts for specific products as well as pursuing an active pricing strategy. This means that while we can generally assume that demand follows a specific type of probability distribution, its parameters are unique to the instance for which an estimate is required. For example, the probability distribution governing the demand of a particular item is specific to the item, date, and retail location for which the forecast is made, and depends on a wide range of further influencing factors.

The remainder of the paper is organized as follows: We first review the relevant literature and existing work in sec. \ref{sec:LitRev}. We then describe our method to predict individual negative binomial PDFs by means of a parametric approach including two distinct machine learning models for mean of variance in sec. \ref{sec:pdfEstimation}. After that, we describe methods for the qualitative and quantitative evaluation of PDF predictions in sec. \ref{sec:pdfEvaluation}. And finally, we present a demand forecasting example to show an application of our methods in sec. \ref{sec:example}.
